Lynott et al. (2014) - Potential error in statistics reporting

### 2017-11-10 manuscript.Rmd
minor change to R code in Example 1

@Banerjee2012 reported that `r orig.N` participants who had been asked to describe an unethical deed from their past judged the room to be darker than participants who had been asked to describe an ethical deed ($M_{unethical}= `r orig.m1`$, ${SD}_{unethical}= `r orig.sd1`$, $M_{ethical}=`r orig.m2`$, ${SD}_{ethical}=`r orig.sd2`$, $t(`r orig.df`)= `r orig.t`$, $p= `r orig.p`$, $d= `r orig.d`$). A close replication by @Brandt2014 with `r rep.n1+rep.n2` participants found no significant effect ($t(`r rep.df`)=`r rep.t`$, $p=`r rep.p`$, $d=`r rep.d`$). Following the small telescopes approach, we can calculate the effect size the original study had 33% power to detect --- $d = `r round(d.33, 2)`$ --- and use this as our SESOI. If we run a TOST with Welch's *t*-test for independent samples and equivalence bounds of ${\Delta}_L=`r round(-d.33, 2)`$ and ${\Delta}_U=`r round(d.33, 2)`$, we indeed find that the effect reported by the replication study is statistically equivalent, $t(`r round(Brandt$TOST_df, 2)`)=`r round(min(Brandt$TOST_t1, Brandt$TOST_t2), 2)`$, $p=`r round(max(Brandt$TOST_p1, Brandt$TOST_p2), 3)`$ (Figure 2A).

>>>>

@Banerjee2012 reported that `r orig.N` participants who had been asked to describe an unethical deed from their past judged the room to be darker than participants who had been asked to describe an ethical deed ($M_{unethical}= `r orig.m1`$, ${SD}_{unethical}= `r orig.sd1`$, $M_{ethical}=`r orig.m2`$, ${SD}_{ethical}=`r orig.sd2`$, $t(`r orig.df`)= `r orig.t`$, $p= `r round(orig.p, 3)`$, $d= `r orig.d`$). A close replication by @Brandt2014 with `r rep.n1+rep.n2` participants found no significant effect ($t(`r round(rep.df, 2)`)=`r round(rep.t, 2)`$, $p=`r round(rep.p, 3)`$, $d=`r round(rep.d, 2)`$). Following the small telescopes approach, we can calculate the effect size the original study had 33% power to detect --- $d = `r round(d.33, 2)`$ --- and use this as our SESOI. If we run a TOST with Welch's *t*-test for independent samples and equivalence bounds of ${\Delta}_L=`r round(-d.33, 2)`$ and ${\Delta}_U=`r round(d.33, 2)`$, we indeed find that the effect reported by the replication study is statistically equivalent, $t(`r round(Brandt$TOST_df, 2)`)=`r round(min(Brandt$TOST_t1, Brandt$TOST_t2), 2)`$, $p=`r round(max(Brandt$TOST_p1, Brandt$TOST_p2), 3)`$ (Figure 2A).
